Choose a License

### 2024-12-10 choose_license.qmd
Add newline again
Add emphasis

  subgraph "License for individual data entries (content)"
  existing_license_content --"No, we created the content<br>entirely by ourselves."--> facts("Entries are facts<br>(like measurements<br>or metadata)?")
  existing_license_content --"Yes, it was<br>shared under a<br>free/open license."--> use_existing_license_content["<em>Use that license</em>"]
  facts --"Yes"--> cc0_content_metadata["CC0 1.0"]
  facts --"No"--> choose_license["<em>Consult flowchart for<br>software, writing,<br>image, audio, and video</em>"]
  end

  subgraph "License for combination of data (database)"
  choose_license --> switch_license["<em>Depending on<br>content license</em>"]
  use_existing_license_content --> switch_license

>>>>

  subgraph content["<strong>License for content</strong>"]
  existing_license_content --"No, we created the content<br>entirely by ourselves."--> facts("Entries are facts<br>(like measurements<br>or metadata)?")
  existing_license_content --"Yes, it was<br>shared under a<br>free/open license."--> use_existing_license_content["<em>Use that license</em>"]
  facts --"Yes"--> cc0_content_metadata["CC0 1.0"]
  facts --"No"--> choose_license["<em>Consult flowchart for<br>software, writing,<br>image, audio, and video</em>"]
  end

  subgraph database["<strong>License for database</strong>"]
  choose_license --> switch_license["<em>Depending on<br>content license</em>"]
  use_existing_license_content --> switch_license
